---
title: "R Notebook"
output: html_notebook
---

# The main objective is to merge all of our data. The 'Player' variable will be our identifier variable for the data set and will be used as the common key variable to merge the data sets. Our penatlies stas did not contain the entire player name so that will be accounted for.

# The 'base' variable in dataframe df will be the target variable when it comes to modeling, so df will be the starting dataframe to which other data sets will be merged.

# There are a couple things that need to be addressed: 

# (1) Make any duplicate entries in the 'Player' variable in df unique.
# (2) Check for any of the 'Player' values addressed in (1) in any of the data sets to be added, and address those if possible
# (3) Check for any duplicate values, or NULL data, in the 'Player' variable in the data sets to be added, and address
# (4) Add a suffix to the non-'Player' variables in the additional data sets incase there are any matching variable names among the datasets and also for ease of use (for example, 'Avg' is seen as a variable name in multiple data sets)
# (5) After data is combined, export the data in a new .csv file


```{r}

#load packages
load.libraries <- c('tidyverse')
install.lib <- load.libraries[!load.libraries %in% installed.packages()]
for(libs in install.lib) install.packages(libs, dependences = TRUE)
sapply(load.libraries, require, character = TRUE)

```



```{r}
# import data

df <- read.csv(file = "datasets/player_contract_2020.csv") 

df_exp <- read.csv(file = "datasets/player_exp_2022.csv") 

df_fg <- read.csv(file = "datasets/stats_fg_2020.csv") 

df_fumb <- read.csv(file = "datasets/stats_fumb_2020.csv") 

df_int <- read.csv(file = "datasets/stats_int_2020.csv") 

df_ko <- read.csv(file = "datasets/stats_ko_2020.csv") 

df_kor <- read.csv(file = "datasets/stats_kor_2020.csv") 

df_pass <- read.csv(file = "datasets/stats_pass_2020.csv") 

df_pr <- read.csv(file = "datasets/stats_pr_2020.csv") 

df_punt <- read.csv(file = "datasets/stats_punt_2020.csv") 

df_rec <- read.csv(file = "datasets/stats_rec_2020.csv") 

df_rush <- read.csv(file = "datasets/stats_rush_2020.csv") 

df_tack <- read.csv(file = "datasets/stats_tack_2020.csv") 

df_pen <- read.csv(file = "datasets/stats_pen_2020.csv")

```




# Start by examining and addressing duplicates in first dataframe, df

```{r}
paste("There are ", length(df$Player) - length(unique(df$Player)), " duplicate player names")



# looking for the duplicates
dups <- df$Player[duplicated(df$Player)]

dups <- df[df$Player %in% dups,] %>% 
        arrange(Player, pos)





#for our duplicates, we will combined the Player and pos values (player name and position)
df[df$Player %in% dups$Player, ]$Player <- paste(df[df$Player %in% dups$Player, ]$Player, " ", df[df$Player %in% dups$Player, ]$pos)


paste("There are ", length(df$Player) - length(unique(df$Player)), " duplicate player names")


# we will also save dataframes dups and dups_fixed to be used to find and address
# any of these players found in other data sets, so we can merge the appropriate stats to the correct Player
dups_fixed <- dups

dups_fixed$Player <- paste(dups_fixed$Player, " ", dups_fixed$pos)


# re-indexed our dataframe keys to be used later
rownames(dups) <- NULL
rownames(dups_fixed) <- NULL


```



```{r}

# next is df_exp

paste("There are ", length(df_exp$Player) - length(unique(df_exp$Player)), " duplicate player names")



# looking for the duplicates
dups_temp <- df_exp$Player[duplicated(df_exp$Player)]

df_exp[df_exp$Player %in% dups_temp, ]


```

# since it is a small number, it is easy to verify correct entries and create list of entries to be removed

# manually verified the experience for the players above and discover which observations to be removed

```{r}

#rows to be removed
remove <- c(64, 156, 181, 619, 740, 762, 1204, 1250, 1251, 1334, 1341, 1453, 1467, 1611, 1615, 1902, 2566, 2598)

df_exp <- df_exp[-remove,]

```


# Create a few functions to help the process


```{r}

# helper function to return rows 
# with Player names matching list of names 'dups'

#will help find rows needing correction due to our original duplicate player names

find_dups <- function(df, dups) {
  
  if (length(df[df$Player %in% dups$Player,]$Player)==0) {
    return(NULL)
  }
  
  return(df[df$Player %in% dups$Player,])
  
}


# helper function append column names
change_names <- function(df, add_on) {
  
  names(df)[2:ncol(df)] <- paste(names(df)[2:ncol(df)], add_on, sep = "_")
  
  return(df)
  
}

```



```{r}

#Find the correct players from our fixed duplicates in original dataframe


find_dups(df_exp, dups)


# correct the names with our dups_fixed list

df_exp[df_exp$Player %in% dups$Player,]$Player <- c(dups_fixed[6,]$Player, dups_fixed[1,]$Player, dups_fixed[4,]$Player)

find_dups(df_exp, dups_fixed)

```



```{r}
#df_exp is ready so left join the dataframe by Player

df <- merge(x=df, y= df_exp, by="Player", all.x=TRUE)
```


```{r}

#since the experience stat is taken from before the 2022 season and other stats data is from the 2020 season, we will remove three years from the experience 

head(df[which(!is.na(df$exp)),] %>% arrange(exp, desc = FALSE))

df$exp <- df$exp - 3


head(df[which(!is.na(df$exp)),] %>% arrange(exp, desc = FALSE))
```

# Processing and adding df_fg data

```{r}

# next is dataframe df_fg

# add suffix to column names
df_fg <- change_names(df_fg, "fg")

#check for duplicate names
find_dups(df_fg, dups)


# merge data
df <- merge(x=df, y=df_fg, by = "Player", all.x = TRUE)

```

# Processing and adding df_fumb stats

```{r}



# add suffix to column names
df_fumb <- change_names(df_fumb, "fumb")

#check for matches to our master duplicate names
find_dups(df_fumb, dups)

#no easy way to determine the correct player so will remove names matching our original corrected names

df_fumb <- df_fumb[!(df_fumb$Player %in% dups$Player),]

find_dups(df_fumb, dups)




```

```{r}


# checking for and fixing df_fumb duplicate Players of its own

paste("There are ", length(df_fumb$Player) - length(unique(df_fumb$Player)), " duplicate player names")


dups_temp <-  df_fumb[duplicated(df_fumb$Player), ]

# again dups_temp is a portion of df_fumb of only entries with duplicate Players

dups_temp <- df_fumb[df_fumb$Player %in% dups_temp$Player,]



```
```{r}
# There are Players with null data represented as an empty string

# Remove those from both dups_temp and df_fumb

dups_temp <- subset(dups_temp, Player!= "")

df_fumb <- subset(df_fumb, Player!= "")

```


```{r}
# fixing double Player entries in df_fumb

# see that all duplicate players have duplicate stats except for Player "David Long"
dups_temp %>%  group_by(Player) %>%  
                 summarise("stat_one" = length(unique(FF_fumb)), "stat_two" = length(unique(FR.TD_fumb)), "stat_three" = length(unique(FR_fumb))) %>% 
                    subset(stat_one > 1 | stat_two > 1 | stat_three > 1)

```

```{r}

# remove duplicates
df_fumb <- df_fumb[!duplicated(df_fumb),]

# re-index
rownames(df_fumb) <- NULL

# check David Long
df_fumb[df_fumb$Player == "David Long", ]


# remove David Long entry with zero stats
df_fumb <- df_fumb[-c(950),]

paste("There are ", length(df_fumb$Player) - length(unique(df_fumb$Player)), " duplicate player names")

```

```{r}
# add df_fumb stats to df using left join

df <- merge(x=df, y=df_fumb, by = "Player", all.x=TRUE)
```


# Processing and adding df_int

```{r}
# add suffix to stats variables
df_int <- change_names(df_int, "int")



```


```{r}

# check for Players in df_int that match our master duplicate list to address if needed
find_dups(df_int, dups)

paste("There are ", length(df_int$Player) - length(unique(df_int$Player)), " duplicate player names")

```

```{r}

# left join df and df_int

df <- merge(x=df, y = df_int, by = "Player", all.x = TRUE)
```


# processing and adding df_ko data


```{r}

# add suffix to df_ko variables

df_ko <- change_names(df_ko, "ko")

```

```{r}

# check for Players in df_int that match our master duplicate list to address if needed
find_dups(df_ko, dups)


paste("There are ", length(df_int$Player) - length(unique(df_int$Player)), " duplicate player names")
```

```{r}
# "Chris Jones" was found in our original master dups list so this must be fixed.
# since we are looking at kick-off stats, we know this is the Chris Jones punter
# so replace the Player name with corresponding name from dups_fixed

df_ko[df_ko$Player == "Chris Jones", ]$Player <- dups_fixed[2,]$Player
```


```{r}
# left join df and df_ko

df <- merge(x=df, y=df_ko, by = "Player", all.x = TRUE)


```


# Processing and adding df_kor data

```{r}
# add suffic to variable names
df_kor <- change_names(df_kor, "kor")


# check for Players in df_kor that match our master duplicate list to address if needed
find_dups(df_kor, dups)


paste("There are ", length(df_kor$Player) - length(unique(df_kor$Player)), " duplicate player names")
```

```{r}

# after verifying there are NULL entries in df_kor noted with Player values equal to an empty string (""), we can remove those

df_kor <- subset(df_kor, Player!= "")

paste("There are ", length(df_kor$Player) - length(unique(df_kor$Player)), " duplicate player names")
```

```{r}

# left join df and df_int

df <- merge(x=df, y = df_kor, by = "Player", all.x = TRUE)
```


# Processing and adding df_pass

```{r}
# add suffic to variable names
df_pass <- change_names(df_pass, "pass")


# check for Players in df_pass that match our master duplicate list to address if needed
find_dups(df_pass, dups)


paste("There are ", length(df_pass$Player) - length(unique(df_pass$Player)), " duplicate player names")
```

```{r}
# we found "Chris Jones" in df_pass which must be corrected with Player data from dups_fixed
# we see Chris Jones only attempted one pass. We will use our Chris Jones that was a kicker, instead of defensive tackle

df_pass[df_pass$Player == "Chris Jones",]$Player <- dups_fixed[2,]$Player
```


```{r}

# addressing the duplicates in df_pass

dups_temp <-  df_pass[duplicated(df_pass$Player), ]

# again dups_temp is a portion of df_fumb of only entries with duplicate Players

dups_temp <- df_pass[df_pass$Player %in% dups_temp$Player,]


```

```{r}
# remove duplicates
df_pass <- df_pass[!duplicated(df_pass),]

# re-index
rownames(df_pass) <- NULL

paste("There are ", length(df_pass$Player) - length(unique(df_pass$Player)), " duplicate player names")

```

```{r}

# left join df and df_pass
df <- merge(x=df, y=df_pass, by = "Player", all.x = TRUE)
```

# Processing and adding df_pr

```{r}
# add suffic to variable names
df_pr <- change_names(df_pr, "pr")


# check for Players in df_pass that match our master duplicate list to address if needed
find_dups(df_pr, dups)


paste("There are ", length(df_pr$Player) - length(unique(df_pr$Player)), " duplicate player names")
```

```{r}

# address duplicate player names 

# remove duplicates
df_pr <- df_pr[!duplicated(df_pr),]

# re-index
rownames(df_pr) <- NULL

paste("There are ", length(df_pass$Player) - length(unique(df_pass$Player)), " duplicate player names")

```
```{r}

# inner join df and df_pr
df <- merge(x=df, y=df_pr, by = "Player", all.x = TRUE)
```


# Processing and adding data from df_punt

```{r}

# add suffic to variable names
df_punt <- change_names(df_punt, "punt")


# check for Players in df_pass that match our master duplicate list to address if needed
find_dups(df_punt, dups)

paste("There are ", length(df_punt$Player) - length(unique(df_punt$Player)), " duplicate player names")

```

```{r}
# "Chris Jones" matched our master duplicate names so will replace with Player data from the punter Chris Jones from dups_fixed

df_punt[df_punt$Player == "Chris Jones", ]$Player <- dups_fixed[2,]$Player
```

```{r}

# left join df and df_punt by Player
df <- merge(x=df, y=df_punt, by= "Player", all.x = TRUE)


```


# Processing and adding data from df_rec

```{r}

# add suffic to variable names
df_rec <- change_names(df_rec, "rec")


# check for Players in df_pass that match our master duplicate list to address if needed
find_dups(df_rec, dups)

# remove null data
df_rec <- subset(df_rec, Player!= "")


paste("There are ", length(df_rec$Player) - length(unique(df_rec$Player)), " duplicate player names")

```

```{r}
#"Michael Thomas" and "Ryan Griffin" were found and must be corrected with dups_fixed
# since we are in reception stats, "Michael Thomas WR" and "Ryan Griffin TE" will be used to replace

df_rec[df_rec$Player == "Michael Thomas", ]$Player <- dups_fixed[4,]$Player

df_rec[df_rec$Player == "Ryan Griffin", ]$Player <- dups_fixed[6, ]$Player


```


```{r}

# left join data
df <- merge(x=df, y=df_rec, by="Player", all.x = TRUE)
```


# Processing and adding df_rush data

```{r}

# add suffic to variable names
df_rush <- change_names(df_rush, "rush")


# check for Players in df_pass that match our master duplicate list to address if needed
find_dups(df_rush, dups)

# remove null data
df_rush <- subset(df_rush, Player!= "")


paste("There are ", length(df_rush$Player) - length(unique(df_rush$Player)), " duplicate player names")

```
```{r}

#"Michael Thomas" and "Chris Jones" were found and must be correct with dups_fixed
# since we are in rush stats, "Michael Thomas SS" and "Chris Jones P" will be used to replace

df_rec[df_rush$Player == "Michael Thomas", ]$Player <- dups_fixed[3,]$Player

df_rec[df_rush$Player == "Chris Jones", ]$Player <- dups_fixed[2, ]$Player


```

```{r}

# left join
df <- merge(x=df, y=df_rush, by="Player", all.x = TRUE)
```

# Processing and adding df_tack data


```{r}

# add suffix to variable names
df_tack <- change_names(df_tack, "tack")


# remove null data
df_tack <- subset(df_tack, Player!= "")

rownames(df_tack) <- NULL


# check for Players in df_tack that match our master duplicate list to address if needed
find_dups(df_tack, dups)


paste("There are ", length(df_tack$Player) - length(unique(df_tack$Player)), " duplicate player names")

```

```{r}

#two "Chris Jones" entries, "Michael Thomas" and "Ryan Griffin" were found and must be correct with dups_fixed
# since we are in tackle stats, "Chris Jones DT" will be used for the "Chris Jones" with higer Tackle stats and "Chris Jones P" for the other entry, "Chris Jones P" will be used to replace the other entry
#also using "Michael Thomas SS" and "Ryan Griffin TE" for the other entry
# it is not clear which Ryan Griffin to use but seems like a TE will be more likely to get tackles than a QB


df_tack[352, ]$Player <- dups_fixed[1,]$Player


df_tack[df_tack$Player == "Michael Thomas", ]$Player <- dups_fixed[3,]$Player

df_tack[df_tack$Player == "Chris Jones", ]$Player <- dups_fixed[2, ]$Player


df_tack[df_tack$Player == "Ryan Griffin", ]$Player <- dups_fixed[6,]$Player

```



```{r}
# address duplicate player names 

# remove duplicates
df_tack <- df_tack[!duplicated(df_tack),]

# re-index
rownames(df_tack) <- NULL

paste("There are ", length(df_tack$Player) - length(unique(df_tack$Player)), " duplicate player names")
```


```{r}
#set up a list of our remaining duplicates in df_tack to see how to address

dups_temp <-  df_tack[duplicated(df_tack$Player), ]

# again dups_temp is a portion of df_fumb of only entries with duplicate Players

dups_temp <- df_tack[df_tack$Player %in% dups_temp$Player,]


```


```{r}


dups_temp

# We are looking at tackles data.
# Since our "Lamar Jackson" is a QB, we will remove the "Lamar Jackson" with 28 comb_tack
# There is no "David Long" in df so it can be ignored
# Our "Brandon Williams" is a DT so will keep the stats with 33 comb_tack
# Our "Josh Allen" is a DE so will keep the stats with 13 comb_tack

# using our observations above, create list of entries to be removed from df_tack

remove <- c(437, 1161, 1447)

df_tack <- df_tack[-remove,]
```



```{r}

# left join data
df <- merge(x=df, y=df_tack, by="Player", all.x = TRUE)
```


# Processing and adding penalty data

```{r}

# need to create a variable target1 in both data frames
# target1 will be the first letter of player name, then the last name, then the team all separated by " "

#example "P Peterson ARI"
 

# helper function to revalue variable values
#revalue function
my_revalue <- function(x, ...){
  reval <- list(...)

  from <- names(reval)
  to <- unlist(reval)

  out <- eval(parse(text= paste0("{", paste0(paste0("x[x ==", "'", from,"'", "]", "<-", "'", to, "'"), collapse= ";"), ";x", "}")))

  return(out)
}


#change data in variable Team in penalties to match df$team

df_pen$Team <- my_revalue(df_pen$Team, "Arizona" = "ARI", "Atlanta"="ATL", "Baltimore"="BAL", "Buffalo" ="BUF", "Carolina" = "CAR", "Chicago"="CHI", "Cincinnati"="CHI", "Cincinnati"="CIN", "Cleveland"="CLE", "Dallas"="DAL", "Denver"="DEN", "Detroit"="DET", "Green Bay" = "GB", "Houston" = "HOU", "Indianapolis" = "IND", "Jacksonville" = "JAC", "Kansas City" = "KC", "LA Chargers" = "LAC", "LA Rams" = "LAR", "Las Vegas" = "LV", "Miami" = "MIA", "Minnesota" = "MIN", "New England" = "NE", "New Orleans" = "NO", "N.Y. Giants" = "NYG", "N.Y. Jets" = "NYJ", "Philadelphia" = "PHI", "Pittsburgh" = "PIT", "Seattle" = "SEA", "San Francisco" = "SF", "Tampa Bay"= "TB", "Tennessee" = "TEN", "Washington" = "WAS")



# create target1 and target2 variables in df_pen for first letter and last name respectively
df_pen <- df_pen %>% mutate(target1 = substring(df_pen$Player, 1, 1), target2 = substring(df_pen$Player, 3, length(df_pen$Player)))


# correct other stats names so there is no duplicate in the df
names(df_pen)[4:(ncol(df_pen)-2)] <- paste(names(df_pen)[4:(ncol(df_pen)-2)], "_pen", sep = "")

# combine elements for target1
df_pen$target1 <- paste(df_pen$target1, df_pen$target2, df_pen$Team, sep = " ")

#columns we don't need
col_remove <- c("Player", "target2", "Team", "Pos")

#remove the columns
df_pen <- df_pen[,!(names(df_pen) %in% col_remove)]
 


```


```{r}

# create new variables of first and last name in df
df[,c(ncol(df) + 1, ncol(df) + 2)] <-  str_split_fixed(df$Player, " ", 2)


# name our new variables
names(df)[(ncol(df) - 1):ncol(df)] <- c("target1", "target2")

# only get the first letter of first name
df$target1 <- substr(df$target1, 1, 1)

# combine elements for new target1
df$target1 <- paste(df$target1, df$target2, df$team, sep = " ")


```



```{r}

# left join data by target1
df <- merge(x=df, y=df_pen, by="target1", all.x = TRUE)


# remove target1
col_remove <- c("target1", "target2")

df <- df[,!(names(df) %in% col_remove)]

# sort by the player name
df <- df[order(df$Player),]

# reset index
row.names(df) <- NULL
```




# All data has be combined, now export the data to new .csv file

```{r}
# export data to cvs files

write.csv(df, "datasets/NFL_2020_stats.csv", row.names=FALSE)
```

